### 2020-12-21 main.tex
Initial Overleaf Import

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Scientific Reports Title to see here}

\author[1,*]{Alice Author}
\author[2]{Bob Author}
\author[1,2,+]{Christine Author}
\author[2,+]{Derek Author}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{corresponding.author@email.example}

\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The demand for sharing and reusing of MD simulation data is increasing, but practical solution remains unclear due to unsolved issues in data storage and indexing.
Here we present a solution for lipid bilayers based on overlay databank structure..

%The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

\section*{Results}

Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}

Topical subheadings are allowed.

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Hao:gidmaps:2014}.

For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{stream}
\caption{Legend (350 words max). Example legend text.}
\label{fig:stream}
\end{figure}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
Condition & n & p \\
\hline
A & 5 & 0.1 \\
\hline
B & 10 & 0.01 \\
\hline
\end{tabular}
\caption{\label{tab:example}Legend (350 words max). Example legend text.}
\end{table}

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2021-03-01 Manuscript/main.tex
Update manuscript

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{NMRlipids databank}

\author[1,*]{Anne Kiirikki}
\author[1,*]{O. H. Samuli Ollila}
%\author[1,2,+]{Christine Author}
%\author[2,+]{Derek Author}
\affil[1]{University of Helsinki, Institute of Biotechonology, Helsinki, Finland}
%\affil[2]{Affiliation, department, city, postcode, country}

\affil[*]{samuli.ollila@helsinki.fi}

%\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
We present a databank of lipid bilayer simulations from the NMRlipids open collaboration project.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

%\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section{Introduction}

The demand for sharing and reusing of MD simulation data is increasing, but practical solution remains unclear due to unsolved issues in data storage and indexing.
Here we present a solution for lipid bilayers based on overlay databank structure.

%The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

\section{Results}

%Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.

\subsection{Quality evaluation of force fields}

The quality of each simulation is evaluated against NMR order parameters.
Indexing of experimental data to automatize evaluation is currently in progress by Anne Kiirikki.

\subsection{Water permeability across membranes}

Averaging water density profiles over all simulations in the databank enables us to calculate the barrier for the water penetration through lipid bilayers.

\subsection{Spin relaxation rates of confined water close to membranes}

Usefulness of the databank beyond MD simulation experts is demonstrated by analysing water spin relaxation times close to bilayers which are used in MRI imaging.

%Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

%\begin{itemize}
%\item First item
%\item Second item
%\end{itemize}

%\subsubsection*{Third-level section}

%Topical subheadings are allowed.

\section{Discussion}

%The Discussion should be succinct and must not contain subheadings.

\section{Methods}

%Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\subsection{Structure of the databank}

NMRlipids databank is a overlay databank composed of index files containing information on the location of original data and all essential information on simulations needed in further use and automatic analysis. Each simulation system is identified using the hash of original trajectory and topology file. The index files are stored in folder structure based on the identity codes of the simulations.

\subsection{Analysis of the data in databank}

Index files in the datanbank contain all the essential information to perform analyses from the simulations. Systems under interest can be selected automatically browsing the index files and filtering the desired properties.

Analysis results can be most conveniently stored to a new datanbank with identical indexing as the original databank. The results can be then easily shared and browsed indentically to the original databank.

\subsection{Indexing the simulation data}

%\subsubsection*{AddData.py}
AddData.py is a script that builds a database that contains a dictionary file and analysis data of each simulation. The dictionary file contains information about the simulation. The script also calculates order parameters of all CH bonds of the lipids in the simulation. To add a simulation it must be first uploaded to Zenodo (www.zenodo.org). The trajectory and topology files of the simulation are downloaded to the working directory from Zenodo but these are not saved into the database. To add a simulation to the database the user has to give some essential information about the simulation. This is done by writing a info file (*INFO.py) which is passed to AddData.py. 
\newline \\
AddData.py requires GROMACS and MDAnalysis library to be installed.
\newline \\
Run AddData.py as follows:
\newline \\
python3 AddData.py exampleINFO.py
\newline \\
There is also a script runAddData.sh that can be used to loop over several info files to add many simulations at one go.

%\subsubsection*{Simulation dictionary}
A simulation dictionary contains information about the simulation. Some of the information is provided by the user. The numbers of lipid molecules, solvent and ions are automatically read from the files and so are the simulation temperature and trajectory length. All this information is saved to a file named README.yaml.

\subsubsection{Compulsory user input}
The following parameters are compulsory and have a strict format.

\subsubsection*{DOI}
DOI is the DOI access number of the simulation. Use the version DOI on Zenodo.

\subsubsection*{MAPPING}
MAPPING provides the name of the mapping file for a lipid. It must be given as a string of alternating lipid name and the corresponding mapping file name separated by a comma. The existing mapping files are in the directory named "mapping\_files". If a mapping file of a certain lipid does not exist the user must construct it.
\newline \\
The purpose of a mapping file is to circumvent the problem caused by different atom naming conventions used by different force fields. The first column of a mapping file contains general atom names. The second column contains the name of the atom as it is in the force field. If the lipid consists of several residues which is the case with some AMBER force fields, then a third column is needed which contains the name of the residue to which each atom belongs to.

\subsubsection*{SOFTWARE}
SOFTWARE stands for the name of the software used for running the simulation. The options are GROMACS, AMBER, NAMD, CHARMM and OPENMM. So far, only simulations run with GROMACS are accepted by the script.

\subsubsection*{TRJ}
TRJ stands for the name of the trajectory file.
\subsubsection*{TPR}
TPR stands for the name of the topology file.

\subsubsection*{PREEQTIME}
PREEQTIME means the time used for pre-equilibrating the system. This should be in nano seconds. 
\subsubsection*{TIMELEFTOUT}
TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation. This value is used in the script to leave out the given length from the analysis!

\subsubsection*{UNITEDATOM}
The handling of united atom simulations is enabled by a separate script called buildH\_calcOP.py. In case of a united atom simulation, the user has to give the names of the lipids and the corresponding names of those lipids as they are in the dic\_lipids.py dictionary used by buildH\_calcOP.py script. In case of an all atom simulation this can be given as an empty string.

\subsubsection*{Molecule names}
The databank has default names for lipids, ions and solvent. The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank. The names provided by the user must be the same as in the tpr file. If a lipid consists of more than one residue the name of the head group residue is given. If the name of the molecule is not in the databank it needs to be added. The names of the molecules are listed in dictionaries called lipids\_dict and molecules\_dict which are in the script. If a new molecule is added it needs to be added to molecule\_numbers\_dict and molecule\_ff\_dict too.

\subsubsection*{dir\_wrk}
The user has to give the path of the working directory.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%free form parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Free form user input}
The form of how the values of these parameters are written is not essential for the script to work properly.
\subsubsection*{SYSTEM}
SYSTEM is name of the system.
\subsubsection*{FF}
FF is the name of the forcefield used in the simulation.
\subsubsection*{FF\_SOURCE}
FF\_SOURCE tells where the forcefield parameters are taken from.
\subsubsection*{FF\_DATE}
FF\_DATE is the date when the forcefield parameters were created. The format is day/month/year.
\subsubsection*{Individual force field names for molecules}
The user can also give forcefield names to different molecules individually. These parameters are named as FFPOPC, FFPOT, FFSOL etc.

\subsubsection{Automatically analyzed parameters}
The following parameters are read automatically from the trajectory and topology files.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%automatically analyzed parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Molecule numbers}
Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
\newline \\
\noindent Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file.

\subsubsection*{Temperature}
Temperature of the simulation is read from the topology file.

\subsubsection*{Trajectory length}
The length of a trajectory is read from the trajectory file.

\bibliography{sample}

%\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Hao:gidmaps:2014}.

%For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Acknowledgements}

%Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

%To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).

%The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

%\begin{figure}[ht]
%\centering
%\includegraphics[width=\linewidth]{stream}
%%\caption{Legend (350 words max). Example legend text.}
%\label{fig:stream}
%\end{figure}

%\begin{table}[ht]
%\centering
%\begin{tabular}{|l|l|l|}
%\hline
%Condition & n & p \\
%\hline
%A & 5 & 0.1 \\
%\hline
%B & 10 & 0.01 \\
%\hline
%\end{tabular}
%\caption{\label{tab:example}Legend (350 words max). Example legend text.}
%\end{table}

%Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2021-03-01 Scripts/BuildDatabank/AddData.py
Add databank scripts

@@ -1,0 +1,1134 @@
+
+# coding: utf-8
+
+# # Database test
+
+# ## Simulation description file
+
+# In[1]:
+import sys
+import importlib
+import re
+from random import randint
+
+inp = sys.argv[1].split('.')[0]
+print(inp)
+inFile = importlib.import_module(inp, package=None)
+
+
+
+
+
+# ## General Imports
+
+# In[2]:
+
+
+# Working with files and directories
+import os
+
+#For quering webs
+import urllib.request
+from urllib.error import URLError,HTTPError,ContentTooShortError
+
+# From time monitoring
+from tqdm import tqdm
+
+import socket
+
+# Python program to find SHA256 hash string of a file
+import hashlib
+
+# For dealing with excel and cvs 
+import pandas as pd
+pd.set_option('display.max_rows', 500)
+pd.set_option('display.max_columns', 500)
+pd.set_option('display.width', 1000)
+pd.set_option('display.max_colwidth', 1000)
+
+#To make real independent copies of lists
+from copy import deepcopy
+
+
+# ## Directories
+
+# In[3]:
+
+
+#dir_wrk = os.path.normpath(dir_wrk)
+dir_wrk = inFile.dir_wrk
+#mapping_dir =os.path.normpath(mapping_dir)
+print(dir_wrk)
+#print(mapping_dir)
+
+
+# ## Check that the DOI link is valid
+
+# In[4]:
+
+
+DOI_url = 'https://doi.org/' + inFile.DOI
+print(DOI_url)
+
+try:
+    response = urllib.request.urlopen(DOI_url)
+    print("Status of the DOI link: {0}".format(response.msg))
+except HTTPError as e:
+    print(DOI_url)
+    print('The server couldn\'t fulfill the request.')
+    print('Error code: ', e.code)
+    user_information = ""
+    print('The code will not proceed, please fix DOI')
+except URLError as e:
+    print(DOI_url)
+    print('We failed to reach a server.')
+    print('Reason: ', e.reason)
+    user_information = ""
+    print('The code will not proceed, please fix DOI')
+else:
+    pass
+
+
+# ## Read input description
+
+# In[5]:
+
+
+bNMRLIPIDS = False #Check if the link contains NMRLIPIDS metadata
+nsims =0 # Counter number of simulations in a submission
+sims = [] #Array with the dictionary containing the information of a simulation
+
[…]

### 2021-03-01 Scripts/BuildDatabank/OrderParameter.py

@@ -1,0 +1,468 @@
+
+#!/usr/bin/env python
+"""
+ calculation of order parameters of lipid bilayers
+ from a MD trajectory
+ 
+ meant for use with NMRlipids projects
+ ------------------------------------------------------------
+ Made by Joe,  Last edit 2017/02/02
+------------------------------------------------------------
+ input: Order parameter definitions
+        gro and xtc file (or equivalents)
+ output: order parameters (2 textfiles)
+--------------------------------------------------------
+"""
+
+# coding: utf-8
+
+import MDAnalysis as mda
+import numpy as np
+import math
+import os, sys
+import warnings
+import re
+
+from optparse import OptionParser
+from collections import OrderedDict
+from operator import add
+from linecache import getline
+
+
+#k_b = 0.0083144621  #kJ/Mol*K
+#f_conc=55430  # factor for calculating concentrations of salts from numbers of ions/waters; in mM/L
+
+bond_len_max=1.5  # in A, max distance between atoms for reasonable OP calculation
+bond_len_max_sq=bond_len_max**2
+
+#%%
+class OrderParameter:
+    """
+    Class for storing&manipulating
+    order parameter (OP) related metadata (definition, name, ...)
+    and OP trajectories
+    and methods to evaluate OPs.
+    """
+    def __init__(self, resname, atom_A_name, atom_B_name, M_atom_A_name, M_atom_B_name, *args):  #removed name, resname from arguments
+        """
+        it doesn't matter which comes first,
+        atom A or B, for OP calculation.
+        """
+#        self.name = name             # name of the order parameter, a label
+        self.resname = resname       # name of residue atoms are in
+        self.atAname = atom_A_name
+        self.atBname = atom_B_name
+        self.M_atAname = M_atom_A_name
+        self.M_atBname = M_atom_B_name
+        self.name = M_atom_A_name + " " + M_atom_B_name # generic name of atom A and atom B
+        for field in self.__dict__:
+            if not isinstance(field, str):
+                warnings.warn("provided name >> {} << is not a string! \n \
+                Unexpected behaviour might occur.")#.format(field)
+            else:
+                if not field.strip():
+                    raise RuntimeError("provided name >> {} << is empty! \n \
+                    Cannot use empty names for atoms and OP definitions.")#.format(field)
[…]

### 2021-03-23 Manuscript/main.tex

@@
 To add a simulation to the database the user has to give some essential information about the simulation.
-This is done by writing a info file (*INFO.py) which is passed to AddData.py.
+This is done by writing a info file (*INFO.yaml) which is passed to AddData.py.
 \newline \\
@@
 \newline \\
-python3 AddData.py exampleINFO.py
+python3 AddData.py -f exampleINFO.yaml
 \newline \\
@@
 
+\subsubsection*{DIR\_WRK}
+DIR\_WRK is the path of the working directory.
+
 \subsubsection*{DOI}
@@
 
-\subsubsection*{MAPPING}
-MAPPING provides the name of the mapping file for a lipid.
-It must be given as a string of alternating lipid name and the corresponding mapping file name separated by a comma.
+\subsubsection*{MAPPING\_DICT}
+MAPPING\_DICT is a dictionary that contains the mapping file names for each lipid in the membrane.
+For each entry in the dictionary the key is the lipid name and the value is the name of the mapping file.
 The existing mapping files are in the directory named "mapping\_files".
@@
 The second column contains the name of the atom as it is in the force field.
-If the lipid consists of several residues which is the case with some AMBER force fields, then a third column is needed which contains the name of the residue to which each atom belongs to.
+If the lipid consists of several residues which is the case in some AMBER force fields, then a third column is needed which contains the name of the residue to which each atom belongs to.
 
@@
 \subsubsection*{TIMELEFTOUT}
-TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation. This value is used in the script to leave out the given length from the analysis!
+TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation. This value is used in the script to discard the given length from the analysis!
 
@@
 In case of a united atom simulation, the user has to give the names of the lipids and the corresponding names of those lipids as they are in the dic\_lipids.py dictionary used by buildH\_calcOP.py script.
-In case of an all atom simulation this can be given as an empty string.
+In the case of an all atom simulation this can be given as an empty string.
 
@@
 
-\subsubsection*{dir\_wrk}
-The user has to give the path of the working directory.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%free form parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Optional and free form user input}
+The form of how the values of these parameters are written is not essential for the script to work properly.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%free form parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Free form user input}
-The form of how the values of these parameters are written is not essential for the script to work properly.
+\subsubsection*{PUBLICATION}
+PUBLICATION stand for the DOI of the associated publication.
+
+\subsubsection*{AUTHORS\_CONTACT}
+The author's contact information can be given if desired.
+
+\subsubsection*{SOFTWARE\_VERSION}
+SOFTWARE\_VERSION stands for the version of the program that was used for running the simulation.
+
 \subsubsection*{SYSTEM}
@@
 FF\_DATE is the date when the forcefield parameters were created. The format is day/month/year.
+\subsubsection*{CPT}
+CPT stands for the name of the cpt file. 
+\subsubsection*{LOG}
+LOG stands for the name of the log file.
+\subsubsection*{TOP}
+TOP stands for the name of the top file.
 \subsubsection*{Individual force field names for molecules}
@@
 The length of a trajectory is read from the trajectory file.
+
+\subsubsection*{Date of running}
+The date of running the script is saved to the README.yaml file.
 

### 2021-03-23 Scripts/BuildDatabank/AddData.py
updated AddData.py

@@ -680,7 +680,7 @@ else:
 
 # In[14]:
 
-socket.setdefaulttimeout(30)
+socket.setdefaulttimeout(15)
 
 download_failed = False
 
@@ -827,21 +827,34 @@ if sim.get('UNITEDATOM'):
 
 tpr = str(dir_tmp) + '/' + str(sim.get('TPR')).translate({ord(c): None for c in "']["})
 trj = str(dir_tmp) + '/' + str(sim.get('TRJ')).translate({ord(c): None for c in "']["})
+#structure_file = ""
+gro = str(dir_tmp) + '/conf.gro'
 
 # OTHER SOFTWARES THAN GROMACS!!!!
 
-#if sim['SOFTWARE'] == gromacs:
-gro = str(dir_tmp) + '/conf.gro'
-    #make gro file
+#if sim['SOFTWARE'] == 'gromacs':
+structure_file = str(dir_tmp) + '/conf.gro'
+#make gro file
 os.system('echo System | gmx trjconv -f '+trj+' -s '+tpr+' -dump 0 -o ' +gro)
-
+    
     # add gro into dictionary for later use
-sim['GRO'] = gro
+sim['GRO'] = structure_file
+    #u_trj = Universe(trj)
+    #u_selection = u_trj.
+    #write('frame_0.gro', frames=u_trj.trajectory[0])
+
+   
+
+#elseif sim['SOFTWARE'] == amber:
+#elseif sim['SOFTWARE'] == namd:
+#elseif sim['SOFTWARE'] == charmm:
+#elseif sim['SOFTWARE'] == openmm:
     
 leaflet1 = 0 #total number of lipids in upper leaflet
 leaflet2 = 0 #total number of lipids in lower leaflet
     
-u = Universe(gro)
+u = Universe(structure_file)
+
 lipids = []
 
 # select lipids 
@@ -997,12 +1010,12 @@ DATAdir = '../../Data/Simulations/' + str(head_dir) + '/' + str(sub_dir1) + '/' 
 # dictionary saved in yaml format
 outfileDICT=str(dir_tmp)+ '/README.yaml'
     
-    #with open(outfileDICT, 'w') as f:
-    #    yaml.dump(sim,f, sort_keys=False)
+with open(outfileDICT, 'w') as f:
+    yaml.dump(sim,f, sort_keys=False)
        
-    #    os.system('cp ' + str(dir_tmp) + '/README.yaml ' + DATAdir)
[…]

### 2021-03-23 Scripts/BuildDatabank/AddData.py
updated AddData.py

@@ -1015,7 +1015,7 @@ with open(outfileDICT, 'w') as f:
        
     os.system('cp ' + str(dir_tmp) + '/README.yaml ' + DATAdir)
  #   outfileDICT.write(str(sim))
-outfileDICT.close()
+#outfileDICT.close()
    
 
 

### 2021-04-08 Scripts/BuildDatabank/AddData.py
Update AddData.py and repository stucture

@@ -1,11 +1,7 @@
+# This is the code that generates databank indexing 
 
-# coding: utf-8
+#IMPORTING LIBRARIES
 
-# # Database test
-
-# ## Simulation description file
-
-# In[1]:
 import sys
 import importlib
 import re
@@ -14,10 +10,6 @@ import argparse
 import yaml
 
 from datetime import date
-
-# ## General Imports
-
-# In[2]:
 
 
 # Working with files and directories
@@ -61,6 +53,7 @@ import sys
 import buildH_calcOP_test
 
 
+
 # Download link
 def download_link(doi, file):
     if "zenodo" in doi.lower():
@@ -85,28 +78,21 @@ with open(input_path) as yaml_file:
     sim = yaml.load(yaml_file, Loader=yaml.FullLoader)
 yaml_file.close()
 
-print(sim)
+# Show the input read
+print("\n Input read from " + input_path + " file:")
+print(yaml.dump(sim))
 
-
-# ## Directories
-
-# In[3]:
-
-
-#dir_wrk = os.path.normpath(dir_wrk)
+# Working directory
 dir_wrk = sim['DIR_WRK']
-#mapping_dir =os.path.normpath(mapping_dir)
-#print(dir_wrk)
-#print(mapping_dir)
 
 
-# ## Check that the DOI link is valid
 
-# In[4]:
 
+
+# Checking that the DOI link is valid
 
 DOI_url = 'https://doi.org/' + sim['DOI']
-print(DOI_url)
+print("Data will be downloaded from: " + DOI_url)
 
 try:
     response = urllib.request.urlopen(DOI_url)
@@ -127,46 +113,13 @@ else:
     pass
 
 
-# ## Read input description
 
-# In[5]:
-
-
-#bNMRLIPIDS = False #Check if the link contains NMRLIPIDS metadata
-#nsims =0 # Counter number of simulations in a submission
-#sims = [] #Array with the dictionary containing the information of a simulation
-
-#for line in inFile.user_information.split("\n"):
-#    if line.strip() == "":
-#        continue
-#    if "#NMRLIPIDS BEGIN" in line:
-#        bNMRLIPIDS = True
-#        continue
-#    if "#NMRLIPIDS END" in line:
-#        bNMRLIPIDS = False
-#        continue
-#    if "@SIM" in line:
-#        #sims.append({"ID" : nsims, "STATUS" : 0})
-#        sims.append({"ID" : nsims})
-#        nsims += 1
[…]

### 2021-04-08 Manuscript/main.tex
Updates from Overleaf

--- 2021-03-01 Manuscript/main.tex
@@
 \usepackage[T1]{fontenc}
-\title{NMRlipids databank}
+\title{NMRlipids Databank}
 
@@
 
-\subsubsection{Compulsory user input}
-The following parameters are compulsory and have a strict format.
+\subsubsection{User input}
+Dictionary variables defined by the user are listed here. 
+The necessary parameters required for the analyses are described first and are marked as ''compulsory''. Then the parameters used to describe the data for further usage and analyses are described.
+While only compulsory parameters are required for the databank entry, strong recommendation is that all the possible parameters would be given to maximize the possibilities to upcycle the contributed data.
 
-\subsubsection*{DOI}
-DOI is the DOI access number of the simulation. Use the version DOI on Zenodo.
+\subsubsection*{DOI (compulsory)}
+Give DOI identity from where the simulation files are located.
+Current databank works only for the data in Zenodo, but other potential sources are may be implemented in the future.
+Note that the DOI must point to a specific version of dataset in Zenodo, i.e., DOI pointing to all versions of certain dataset does not work.
 
-\subsubsection*{MAPPING}
-MAPPING provides the name of the mapping file for a lipid.
-It must be given as a string of alternating lipid name and the corresponding mapping file name separated by a comma.
-The existing mapping files are in the directory named "mapping\_files".
-If a mapping file of a certain lipid does not exist the user must construct it.
-\newline \\
-The purpose of a mapping file is to circumvent the problem caused by different atom naming conventions used by different force fields.
+\subsubsection*{SOFTWARE (compulsory)}
+Give the name of software used to run the simulation. The options are GROMACS, AMBER, NAMD, CHARMM and OPENMM. So far, only simulations run with GROMACS are accepted by the script.
+
+\subsubsection*{TRJ (compulsory)}
+Give the name of the trajectory file that is found from the DOI given above.
+
+\subsubsection*{TPR (compulsory)}
+Give the name of the file with topology information (tpr file in the case of Gromacs) that is found from the DOI given above.
+
+\subsubsection*{PREEQTIME (compulsory)}
+Give the time simulated before the uploaded trajectory in nanoseconds. For example, if you upload 100-200~ns part of total 200~ns simulation, this should value should be 100.
+
+\subsubsection*{TIMELEFTOUT (compulsory)}
+Give the time that should be considered as an equilibration period in the uploaded trajectory.
+Frames before the give time will be discarded in the analysis.
+For example, if you upload 0-200~ns part of total 200~ns simulation where the first 100~ns should be considered as an equilibration, this value should be 100.
+
+\subsubsection*{Molecule names (compulsory)}
+In the databank, each molecule has a unique abbreviation (see table~\ref{tab:abbreviations}). 
+You need to give the residue names of these molecules corresponding your simulation.
+%The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank.
+The names provided by the user must be the same as in the tpr file.
+If atoms in a lipid belong to different residues (typical situation in Amber force fields), give the name of the head group residue here, and add the residue name of each atom to the third column in the mapping file (see below).
+If your simulation contains molecules that are not yet in the databank, you need to define the abbreviation and add molecules to the lipids\_dict, molecules\_dict, molecule\_numbers\_dict and molecule\_ff\_dict in the AddData.py script, as well as to table~\ref{tab:abbreviations}.
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c|c}
+        Abbreviation & Molecule name \\
+        \hline
+        POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine\\
+        POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
+        POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
+        POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
+        CHOL & cholesterol \\
+        DHMDMAB & dihexadecyldimethylammonium \\
+        \hline
+        POT & potassium ion \\
+        SOD & sodium ion \\
+        CLA & chloride ion \\
+        CAL & calcium ion \\
+        SOL & water \\
+    \end{tabular}
+    \caption{Abbreviations used in the databank}
+    \label{tab:abbreviations}
+\end{table}
+
+\subsubsection*{MAPPING\_DICT (compulsory)}
+For the analysis, we need to know the names of atoms in your system.
+These are defined using the mapping file convention introduced in \url{http://nmrlipids.blogspot.com/2015/03/mapping-scheme-for-lipid-atom-names-for.html}, where first column gives the universal atom name, second gives the atom name in force field, and third gives the residue name if not the same for all atoms.
+The name of the mapping file for each molecule needs to be given in dictionary format.
+The dictionary the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the name of the mapping file.
+The already existing mapping files can be found from the directory named "mapping\_files".
+If a mapping file for your molecule(s) do not exist, you need to construct one and add to the "mapping\_files" directory.
+
+%\newline \\
+%The purpose of a mapping file is to circumvent the problem caused by different atom naming conventions used by different force fields.
 The first column of a mapping file contains general atom names.
 The second column contains the name of the atom as it is in the force field.
-If the lipid consists of several residues which is the case with some AMBER force fields, then a third column is needed which contains the name of the residue to which each atom belongs to.
+If the lipid consists of several residues which is the case in some AMBER force fields, then a third column is needed which contains the name of the residue to which each atom belongs to.
 
-\subsubsection*{SOFTWARE}
-SOFTWARE stands for the name of the software used for running the simulation.
-The options are GROMACS, AMBER, NAMD, CHARMM and OPENMM.
-So far, only simulations run with GROMACS are accepted by the script.
+\subsubsection*{DIR\_WRK (compulsory)}
+Give the path of the working directory in your local computer.
+The trajectory and topology files will be downloaded to this trajectory, and temporary files created during processing will be stored here.
 
-\subsubsection*{TRJ}
-TRJ stands for the name of the trajectory file.
-\subsubsection*{TPR}
-TPR stands for the name of the topology file.
+\subsubsection*{UNITEDATOM\_DICT (compulsory for united atom trajectories)}
+Order parameters from united atom simulations are calculated using buildH code (\url{https://github.com/patrickfuchs/buildH}).
+For united atom simulations, you need to tell how hydrogens are added based on definitions in the dic\_lipids.py dictionary.
+This is done by giving a dictionary where the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the correct dictionary key in dic\_lipids.py.
+If correct dictionary key is not yet found, you need to add to dic\_lipids.py.
+In the case of an all atom simulation, UNITEDATOM is left empty.
 
-\subsubsection*{PREEQTIME}
-PREEQTIME means the time used for pre-equilibrating the system. This should be in nano seconds. 
-\subsubsection*{TIMELEFTOUT}
-TIMELEFTOUT stands for the length of the simulation in nano seconds to be left out at the beginning of the simulation. This value is used in the script to leave out the given length from the analysis!
+\subsubsection*{PUBLICATION}
+Give reference to a publication(s) related to the data.
 
-\subsubsection*{UNITEDATOM}
-The handling of united atom simulations is enabled by a separate script called buildH\_calcOP.py.
-In case of a united atom simulation, the user has to give the names of the lipids and the corresponding names of those lipids as they are in the dic\_lipids.py dictionary used by buildH\_calcOP.py script.
-In case of an all atom simulation this can be given as an empty string.
+\subsubsection*{AUTHORS\_CONTACT}
+Give the name and email of the main author(s) of the data.
 
-\subsubsection*{Molecule names}
-The databank has default names for lipids, ions and solvent.
-The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank.
-The names provided by the user must be the same as in the tpr file.
-If a lipid consists of more than one residue the name of the head group residue is given.
-If the name of the molecule is not in the databank it needs to be added.
-The names of the molecules are listed in dictionaries called lipids\_dict and molecules\_dict which are in the script.
-If a new molecule is added it needs to be added to molecule\_numbers\_dict and molecule\_ff\_dict too.
+\subsubsection*{SYSTEM}
+Give description of system in free format. For example ''POPC with cholesterol at 301K''.
 
-\subsubsection*{dir\_wrk}
-The user has to give the path of the working directory.
+\subsubsection*{SOFTWARE\_VERSION}
+Give the version of the software used.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%free form parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Free form user input}
-The form of how the values of these parameters are written is not essential for the script to work properly.
-\subsubsection*{SYSTEM}
-SYSTEM is name of the system.
 \subsubsection*{FF}
-FF is the name of the forcefield used in the simulation.
+Give the name of the force field used used in the simulation.
+
 \subsubsection*{FF\_SOURCE}
-FF\_SOURCE tells where the forcefield parameters are taken from.
+Describe the source of the force field parameters. For example, CHARMM-GUI, link to webpage where parameters were downloaded, or citation to a paper.
+
 \subsubsection*{FF\_DATE}
-FF\_DATE is the date when the forcefield parameters were created. The format is day/month/year.
+Give the date when parameters were accessed or created. The format is day/month/year.
+
 \subsubsection*{Individual force field names for molecules}
-The user can also give forcefield names to different molecules individually. These parameters are named as FFPOPC, FFPOT, FFSOL etc.
+In some cases special force fields are used for certain molecules.
+For example, non-standard parameters for ions or other molecules have been used.
+These can be specified giving forcefield names separately for individual molecules.
+These can be given as parameters named as
+FF+[abbreviation from table \ref{tab:abbreviations}], i.e., FFPOPC, FFPOT, FFSOL etc.
+
+\subsubsection*{CPT (Gromacs)}
+Give the name of the Gromacs checkpoint file that is found from the DOI given above.
+CPT stands for the name of the cpt file.
+
+\subsubsection*{LOG (Gromacs)}
+Give the name of the Gromacs log file that is found from the DOI given above.
+
+\subsubsection*{TOP (Gromacs)}
+Give the name of the Gromacs top file that is found from the DOI given above.
 

### 2021-04-09 Scripts/BuildDatabank/AddData.py
Add data and change AddData.py to give gro instead tpr to MDAnalysis due to the incombability with Gromacs 2021

@@ -134,6 +134,18 @@ lipids_dict = {
             'POPE' : {"REQUIRED": False,
                             "TYPE" : "string",
                         },
+            'DMPC' : {"REQUIRED": False,
+                            "TYPE" : "string",
+                        },
+            'POPI' : {"REQUIRED": False,
+                            "TYPE" : "string",
+                        },
+            'SAPI' : {"REQUIRED": False,
+                            "TYPE" : "string",
+                        },
+            'SLPI' : {"REQUIRED": False,
+                            "TYPE" : "string",
+                        },
             'CHOL' : {"REQUIRED": False,
                             "TYPE" : "string",
                         },
@@ -182,6 +194,18 @@ molecule_numbers_dict = {
             'NPOPE' : {"REQUIRED": False,
                        "TYPE" : "array",
                         },
+            'NDMPC' : {"REQUIRED": False,
+                       "TYPE" : "array",
+                        },
+            'NPOPI' : {"REQUIRED": False,
+                       "TYPE" : "array",
+                        },
+            'NSAPI' : {"REQUIRED": False,
+                       "TYPE" : "array",
+                        },
+            'NSLPI' : {"REQUIRED": False,
+                       "TYPE" : "array",
+                        },
     
             'NCHOL' : {"REQUIRED": False,
                        "TYPE" : "array",
@@ -221,6 +245,18 @@ molecule_ff_dict = {
                                 "TYPE": "string",
                            },
                 'FFPOPE' : {"REQUIRED": False,
+                                "TYPE": "string",
+                           },
+                'FFDMPC' : {"REQUIRED": False,
+                                "TYPE": "string",
+                           },
+                'FFPOPI' : {"REQUIRED": False,
+                                "TYPE": "string",
+                           },
+                'FFSAPI' : {"REQUIRED": False,
+                                "TYPE": "string",
+                           },
+                'FFSLPI' : {"REQUIRED": False,
                                 "TYPE": "string",
                            },
[…]

### 2021-09-13 Scripts/BuildDatabank/QualityEvaluation.py
Update QualityEvaluation.py
Modifications for shitness(TM) scale. Precision issue now patched and works without dubious scaling. The fragment-vise calculation drafted but not fully implemented yet (see comments). IMO the script could use cleaning and should be implemented in a way that the user can switch the quality evalution function easily and to something custom they wrote themselves.

@@ -6,6 +6,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import math
 import argparse
+import decimal as dc
 
 from random import randint
 
@@ -270,22 +271,20 @@ def prob_S_in_g(OP_exp, exp_error, OP_sim, op_sim_sd):
     #normal distribution N(s, OP_sim, op_sim_sd)
     a = OP_exp - exp_error
     b = OP_exp + exp_error
-    P_S = norm.cdf(b, loc=OP_sim, scale=op_sim_sd) - norm.cdf(a, loc=OP_sim, scale=op_sim_sd)
-
-    if OP_exp > 0 or OP_exp < 0:
-        print('experiment OP')
-        print(OP_exp,exp_error)
-        print('simulation OP')
-        print(OP_sim,op_sim_sd)
-        print('b')
-        print(norm.cdf(b, loc=OP_sim, scale=op_sim_sd))
-        print('a')
-        print(norm.cdf(a, loc=OP_sim, scale=op_sim_sd))
-        
-
-        print('P')
-        print(P_S)
-    return P_S
+    #P_S = norm.cdf(b, loc=OP_sim, scale=op_sim_sd) - norm.cdf(a, loc=OP_sim, scale=op_sim_sd)
+    #changing to survival function to increase precision, note scaling. Must be recoded to increase precision still 
+    P_S = -norm.sf(b, loc=OP_sim, scale=op_sim_sd) + norm.sf(a, loc=OP_sim, scale=op_sim_sd)
+    
+    if math.isnan(P_S) :
+      return P_S
+      
+    #this is an attempt to deal with precision, max set manually to 70.
+    dc.getcontext().prec=70
+    precise_log=-dc.Decimal(P_S).log10()
+    	
+    #print("difference of two prec logs",float(foo)+math.log10(P_S)) 
+    	
+    return float(precise_log)
     
 # quality of simulated order parameter
 #def OPquality(P_S,op_sim_STEM):
@@ -335,6 +334,8 @@ def carbonError(OP_sim, OP_exp):
 
 def fragmentQuality(fragment, exp_op_data, sim_op_data):
     p_F = evaluated_percentage(fragment, exp_op_data)
+    #warning, hard coded experimental error
+    exp_error=0.02
     E_sum = 0
     if p_F != 0:
         for key_exp, value_exp in exp_op_data.items():
@@ -342,10 +343,13 @@ def fragmentQuality(fragment, exp_op_data, sim_op_data):
[…]

### 2021-09-14 Manuscript/main.tex

@@
 \usepackage[T1]{fontenc}
+\usepackage{graphicx}
 \title{NMRlipids Databank}
@@
 
-NMRlipids databank is a overlay databank composed of index files containing information on the location of original data and all essential information on simulations needed in further use and automatic analysis.
-Each simulation system is identified using the hash of original trajectory and topology file.
-The index files are stored in folder structure based on the identity codes of the simulations.
+\begin{figure}
+  \includegraphics[width=\textwidth]{figures/DataBankStructure.pdf}
+  \caption{Structure of the NMRlipids databank}\label{DatabankStructure}
+\end{figure}
+
+NMRlipids databank is a overlay databank composed of files that contain all the essential information
+on the molecular dynamics simulation trajectories that are listed in the databank.
+The location publicly avaiable raw MD simulation data is flexible.
+The NMRlipids databank files contain all the essential information on the
+original data that enable wide range of applications.
+%and all essential information on simulations needed in further use and automatic analysis.
+
+Each simulation system is identified using the hash of original trajectory and topology file. The index files are stored in folder structure based on the identity codes of the simulations.
 
